Actual Causes as Changes of State in Continuous Time

### 2021-01-20 docs/resources/CogSci_paper/paper.tex
fig 1 caption

\title{Actual Causes as Changes of State in Continuous Time}

@@

\begin{figure*}
\begin{center}
%\includegraphics[width=7cm]{figures/demo.eps}
\includegraphics{figures/introfig.eps}
\end{center}
\caption{(a) An example of an AND-Gate causal system. In an AND-Gate for an effect to occur it needs the occurence of all the causes it is linked to. Here for the smoke alarm to go off, both the ionization and photoelectric detectors it is connected to have to be activated. In this scenario the detectors activation spreads over the top chain first (ii) and then over the bottom chain leading to the alarm activation (iii).} 
\label{fig:intro}
\end{figure*}

>>>>

%\title{A continuity-based account of actual causation}
%\title{Identifying actual causes by tracking Changes of State in Continuous Time}
\title{Actual Causes as Changes of State in Continuous Time}

@@

\begin{figure*}
\begin{center}
%\includegraphics[width=7cm]{figures/demo.eps}
\includegraphics{figures/introfig.eps}
\end{center}
\caption{(a)(i) A smoke alarm connected to a chain of ionization detectors (top branch) and a chain of photoelectric detectors (bottom branch). All components are initially inactive (ii) Detector \ev{R}{D} activates and activity propagates along the top branch. (iii) Detector \ev{R}{C} activates and ultimately triggers the activation of the alarm, which activates only when both  \ev{I}{D} and \ev{I}{C} are active. (b) An activation sequence in which (i) the top branch activates first, (ii) activation starts and finishes along the bottom branch while activation continues along the top branch, and (iii) the top branch completes its activation and ultimately triggers the smoke alarm.}
\label{fig:intro}
\end{figure*}
